---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# bayesnetworks

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/bayesnetworks)](https://cran.r-project.org/package=bayesnetworks)
<!-- badges: end -->

The goal of bayesnetworks is to do MCMC fitting of Bayesian networks, including source & sink constraints and external network info.

## Installation

<!--
You can install the released version of bayesnetworks from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("bayesnetworks")
```
-->

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("USCbiostats/bayesnetworks")
```
## Examples

The network is fitted by passing in data and network structure

```{r}
library(bayesnetworks)
set.seed(1234)

x <- fit_network(X = network$data,
                 Npar = network$dag_info$Npar,
                 nodetype = network$dag_info$nodetype,
                 par = network$dag_info$par,
                 Niter = 50000)
```

Some diagnostic plots:

```{r}
library(ggplot2)
ggplot(x$mcmc, aes(iter, Nagree)) +
  geom_line(aes(color = "Nagree")) +
  geom_line(aes(y = TotalEdges, color = "TotalEdges")) +
  scale_color_manual(values = c("#B22222", "#22B2B2"))
```

```{r}
ggplot(x$mcmc, aes(iter, FN)) +
  geom_line(aes(color = "FN")) +
  geom_line(aes(y = FP, color = "FP")) +
  scale_color_manual(values = c("#FFA500", "#005AFF"))
```

## Code of Conduct

Please note that the 'bayesnetworks' project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
